Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
social p

<!-- social scale -->
Social scale is essential consideration for social network analysis
[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based social networks
generated using GPS location data use a social distance threshold to define
social associations. Increasing the social distance threshold resulted in an
increase in graph strength across all three habitat layers  (Figure
\@ref(fig:socres)). <!-- This means blah blah for different types of
interactions.--> However, habitat layers differed in their response to
increasing social distance threshold, with open and foraging with a larger
increase in graph strength and greater variation across individuals. <!-- What
could this mean biologically? --> These results emphasize that multilayer
network metrics are directly influenced by social scale. In extension, caribou
relocations could be classified into behavioural states using hidden Markov
models to explore the influence of behavioural states on social scale in a
multilayer network [see @Jones_2020].
<!-- social scale -->

>>>>

<!-- social scale -->
Social scale is essential consideration for social network analysis
[@Castles_2014; @Carter_2015; @Farine_2015a]. For example, networks can be
constructed based on fine-scale social interactions (e.g. grooming or
aggression), social associations (e.g. group membership or proximity), or
spatial or home range overlap. Here, we define social associations in a series
of proximity-based social networks based on a series of social distance
thresholds. <!-- up to here-->Increasing the social distance threshold resulted in an
increase in graph strength across all three habitat layers  (Figure
\@ref(fig:socres)). <!-- This means blah blah for different types of
interactions.--> However, habitat layers differed in their response to
increasing social distance threshold, with open and foraging with a larger
increase in graph strength and greater variation across individuals. <!-- What
could this mean biologically? --> These results emphasize that multilayer
network metrics are directly influenced by social scale. In extension, caribou
relocations could be classified into behavioural states using hidden Markov
models to explore the influence of behavioural states on social scale in a
multilayer network [see @Jones_2020].
<!-- social scale -->
